NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-09-04 paper/main.tex
pdf prepared to be submitted
before preparing final submission

I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\

@@

\textbf{Results:}
Three carb eating day patterns (low/high percentage, and regular meal days) were found in 24483 observation days, based on which three types of carb eaters were defined: low (28.1\%), moderate (28.8\%), and high (43.1\%) carb eaters. On average, low-carb eaters consumed the highest amount of total energy intake (7985.8 kJ), and they had higher percentages of energy contributed by fat and alcohol, especially after 8 pm. Moderate-carb eaters consumed the lowest amount of total energy (7341.8 kJ) while they had the tendency of eating carb later in time-of-day. High-carb eaters consumed most of their carb and energy within time slots of 6-9 am, 12-2 pm and 5-8 pm. In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (adjusted OR: 0.64, 95\%CI: 0.41, 1.01). In women, high-carb eaters who lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, -2.87, -0.73) and WC (-4.71 cm, -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).

>>>>

%I would also like to thank Aichi Medical Univeristy for funding my studentship at the London School of Hygiene and Tropical Medicine. \\

@@

\textbf{Results:}
Three carb eating day patterns (low/high percentage, and regular meal days) were found in 24483 observation days, based on which three types of carb eaters were defined: low (28.1\%), moderate (28.8\%), and high (43.1\%) carb eaters. On average, low-carb eaters consumed the highest amount of total energy intake (7985.8 kJ), and they had higher percentages of energy contributed by fat and alcohol, especially after 8 pm. Moderate-carb eaters consumed the lowest amount of total energy (7341.8 kJ) while they had the tendency of eating carb later in time-of-day. High-carb eaters consumed most of their carb and energy within time slots of 6-9 am, 12-2 pm and 5-8 pm. In men, moderate-carb eaters may have lower odds of having hypertension compared with low-carb eaters (OR: 0.64, 95\%CI: 0.41, 1.01). In women, high-carb eaters who lived with partners had both lower BMI (-1.76 kg/m\textsuperscript{2}, 95\%CI: -2.87, -0.73) and WC (-4.71 cm, 95\%CI: -7.00, -2.43) compared with low-carb eaters, although these inverse associations were not observed in women who lived alone (\textit{p} for interaction 0.014, and 0.009).
